Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-11-08 paper/lncsFormat.tex
before remove \begin{comment}

%\usepackage{showframe}%show the margin
%\usepackage{ulem}%used for uwave
\usepackage{comment}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithmic}

@@

\usepackage{hyperref}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
%\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
\title{Leveraging Knowledge Base for Accurate Event Detection on Microblog Stream}
\titlerunning{Transfer Learning for Accurate Event Detection}
%构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
%\title{Constructing Knowledge Base's Category Topics for Transfer Learning in Accurate Microblog Event Detection}
%\begin{comment}% for double blind
\author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Tengjiao Wang\inst{1} \and Yazhou Wang\inst{1} }
\institute{Key Laboratory of High Confidence Software Technologies (Ministry of Education), EECS, Peking University, Beijing, China \\ 
\path{huangwaleking@gmail.com,{pekingchenwei,tjwang}@pku.edu.cn}\\ 
\path{pkuwangyz@gmail.com}
}
%\end{comment}

@@

Knowledge base can be a good supplementary for event detection on microblog stream.
Different from the not-well-organized microblog stream, knowledge base (e.g. Wikipedia) is constructed elaborately and contains rich information. 
For example, the microblog message ``Possible Ft. Hood Attack Thwarted (2011-07-28)'' is short, but still comprehensible because the words ``\textit{Ft. Hood}" is included in the wiki page ``\textit{Ft. Hood}", and belongs to the category ``\textit{Military}''.
By reading these two wiki pages, the model easily understands the example tweet is talking about something related to \textit{Military}.
In other words, knowledge base enriches the linkages between words, and provides more comprehensive context for microblogs.
Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information restored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.
%拆成两个小图，中间说明这是transfer learning过后的
\intextsep=3pt plus 3pt minus 1pt
\begin{figure}[h]
        \centering
        \includegraphics[width=1.0\columnwidth]{img/hood.pdf}
        %\caption{Hood\footnote{\url{https://en.wikipedia.org/wiki/Naser_Jason_Abdo#Arrest}}\footnote{\url{https://en.wikipedia.org/wiki/Fort_Hood#2011_attack_plot}}}
        \label{fig:hood}
\end{figure}

But it's non-trivial to conduct transfer learning from knowledge base to microblog stream directly.
The existing RDF model\cite{klyne2006rdf} lacks an efficient quick mechanism to transfer the knowledge, since it's mainly designed for managing knowledge as tuples on graph. And the query on large graph is also very expensive\cite{huang2011scalable}, which is not suitable for the scene of quickly and acuaretely detecting events.
What most meet the efficiency demand is Twevent\cite{Twevent2012}, but it's limited to filtering out meaningless microblogs by looking up Wikipedia. Some event,  which may contains the segments not restored in Wikipedia, may be dropped incorrectly.

@@

@@

\intextsep=5pt plus 3pt minus 1pt
\begin{figure}[h]
	\setlength{\abovecaptionskip}{0.cm}
	\setlength{\belowcaptionskip}{0.cm}
	\centering
    \label{fig:subfig} %% label for entire figure
        \subfigure[]{
                \includegraphics[width=.42\columnwidth]{img/NSDetectorExample.pdf}
                \label{fig:modelDesc}

        }
        \subfigure[]{
                \includegraphics[width=.42\columnwidth]{img/initializationExample.pdf}
                \label{fig:NSinitializaton}
        }
        \caption{(a)\textsc{TransDetector}'s process flow, taking \textit{Military} related events in cyberspace as an example. \textsc{TransDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events.;(b)Illustration on how to initialize history states from Wikipedia, taking \textit{Military} as an example.}
\end{figure}

@@

%The reason why this kind methods cannot achieve high precision and high recall simultaneously lies in that they lack the accumulation of history knowledge. 
%This kind methods ``understand" the document only by the recent data and the frequencies of the data, but the ``understanding" is not so confident that they still need the specific threshold to help to make decision.

@@

%近年来，知识图谱也被广泛应用在了文本挖掘领域，TKDE的文章利用wikipedia将

%Although \cite{Wurzer:2015wq} points out that UMass\cite{Allan:2000wu} and its variants\cite{Petrovic:2010uj}\cite{petrovic2012using}\cite{Wurzer:2015wq} are the state-of-art systems on the Event Detection task for the newswire data, these systems still suffers from the lack of accuracy to applied on more general cyberspace data, such as tweets, emails, and reddit posts.

%\textbf{Knowledge Base}. \cite{faralli2015large} propose the Twixonomy Graph.

%Twitter Trending Topic Classification
%We use PageRank-HITS\cite{Yan:2015wq} algorithm to update score of categories in wikipedia.

%3*4 figures, 0-11 is reorganized in the following order: 0, 1, 4, 5, 8, 9;
%2, 3, 6, 7, 10, 11;
\begin{comment}
\begin{figure*}[ht]
        \centering
        \label{fig:subfig} %% label for entire figure
        \subfigure[\((0.25,0.25,0.25)\)]{
                \label{fig:subfig:a} %% label for first subfigure a
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph0.pdf}
        }
        \subfigure[\((0.5,0.5,0.5)\)]{
                \label{fig:subfig:b} %% label for second subfigure b
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph1.pdf}
        } 
        \subfigure[\((0.25,0.25,0.75)\)]{
                \label{fig:subfig:c} %% label for third subfigure c
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph4.pdf}
        }
        \subfigure[\((0.5,0.5,1.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure d
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph5.pdf}
        }
        \subfigure[\((0.25,0.75,0.75)\)]{
                \label{fig:subfig:d} %% label for third subfigure e
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph8.pdf}
        }
        \subfigure[\((0.5,1.5,1.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure f
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph9.pdf}
        }\hspace{1in}
        \subfigure[\((1.5,1.5,1.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure g
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph2.pdf}
        }
        \subfigure[\((2.5,2.5,2.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure h
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph3.pdf}
        }
        \subfigure[\((1.5,1.5,2.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure i
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph6.pdf}
        }
        \subfigure[\((2.5,2.5,3.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure j
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph7.pdf}
        }
        \subfigure[\((1.5,2.5,2.5)\)]{
                \label{fig:subfig:d} %% label for third subfigure k
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph10.pdf}
        }
        \subfigure[\((2.5,3.5,3.5)\)]{
                \label{fig:subfig:a} %% label for first subfigure l
                \includegraphics[height=2.14cm]{img/croppedDirichletGraph11.pdf}
        }\hspace{1in}
        \caption{Illustration of Dirichlet distribution's probabilistic density on the 3-dimensional simplex when given different priors. (a,b,g,h) the left four subfigures illustrate the probabilistic density when given the symetric priors for Dirichlet distribution; (c,d,i,j) the central subfigures illustrate the probablistic density given ; (e,f,k,l) }
\end{figure*}
\end{comment}

\section{Proposed Method}
Knowledge base often contains much information about what happened. 
But the existing RDF model\cite{klyne2006rdf} on knowledge base lacks an efficient mechanism to transfer the information from knowledge base to text stream.  
With the help of knowledge base's structure (detailed in sec \ref{subsec:hs_initialization}), we provide a  lightweight model to transfer the information in knowledge base to text stream.

@@

After processing each time window's data, the words in microblogs can be enriched semantically with knowledge base.
In this way, the transfer learning model provides richer semantics and less noise for microblog stream, which promotes the accuracy of event detection significantly. 
The following definitions are the concepts used by the transfer learning model \textsc{TransDetector}.

@@

\begin{table}
\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
\setlength{\belowcaptionskip}{0.cm}
\centering
\caption{Events about \textit{military} detected by systems between 2011-07-22 and 2011-07-28}
\label{my-label}
\scalebox{0.77}{
\begin{threeparttable}  
\begin{tabular}{|c|l|l|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Date} & \multirow{2}{*}{Event key words} & \multirow{2}{*}{Representative event tweet} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of \\ event tweet\end{tabular}} & \multicolumn{6}{c|}{Methods\tnote{a}} \\ \cline{5-10} 
 &  &  &  & L & TU & TW & E & B & TD \\ \hline
7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman... http://dlvr.it/cLbk8\end{tabular} & 557 & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\ \hline
7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 & - & - & \checkmark &  \checkmark & - & \checkmark \\ \hline
7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 47 & \checkmark & - & \checkmark & \checkmark & - & \checkmark \\ \hline
7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 52 & - & - & - & - & - & \checkmark \\ \hline
7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 & - & - & - & - & - & \checkmark \\ \hline
\end{tabular}

>>>>

\usepackage{showframe}%show the margin
%\usepackage{ulem}%used for uwave
\usepackage{comment}
\usepackage{subfigure}
\usepackage{enumitem}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{algorithmic}

@@

\usepackage{hyperref}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Category-Level Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
%\title{Leveraging Knowledge Base for Accurate Event Detection on Microblog Stream}
\titlerunning{Transfer Learning for Accurate Event Detection}
%构造（building）一个**词表（找一个词对它更合适的描述），for transfer learning in accurate event detection
%\title{Constructing Knowledge Base's Category Topics for Transfer Learning in Accurate Microblog Event Detection}
%\begin{comment}% for double blind
\author{Weijing Huang\inst{1} \and Wei Chen\inst{1} \thanks{Corresponding author.} \and Tengjiao Wang\inst{1} \and Yazhou Wang\inst{1} }
\institute{Key Laboratory of High Confidence Software Technologies (Ministry of Education), EECS, Peking University, Beijing, China \\ 
\path{huangwaleking@gmail.com,{pekingchenwei,tjwang}@pku.edu.cn}\\ 
\path{pkuwangyz@gmail.com}
}
%\end{comment}

@@

Knowledge base can be a good supplementary for event detection on microblog stream to address these challenges.
Different from the not-well-organized microblog stream, knowledge base (e.g. Wikipedia) is constructed elaborately and contains rich information. 
For example, the microblog message ``Possible Ft. Hood Attack Thwarted (2011-07-28)'' is short, but still comprehensible because the words ``\textit{Ft. Hood}" is included in the wiki page ``\textit{Ft. Hood}", and belongs to the category ``\textit{Military}'' at a higher conceptual level.
By regarding these two wiki pages and the word \textit{attack} (also highly related to \textit{Military}), the model easily understands the example tweet is about something related to \textit{Military}.
In other words, knowledge base enriches the linkages between words, and provides more comprehensive context for microblogs.
Since the transfer learning\cite{pan2010survey} aims at utilizing the extra information restored in the source dataset to benefit the target dataset, it provides a feasible way to enhance the event detection in microblog stream.
Taking the below Figure \ref{fig:hood} as an example, the fluctuation of time series of raw word \textit{hood} is not so obvious to reflect the event happened to the military base \textit{Ft. Hood}.
After referring to the knowledge base and extracting the time series of word \textit{``hood"} about \textit{``Military"}, it's more vivid to detect the event happened on July 28th, 2011.

\intextsep=0pt plus 0pt minus 0pt
\begin{figure}[h]
		\setlength{\abovecaptionskip}{0.cm}
        \setlength{\belowcaptionskip}{0.cm}
        \centering
        \includegraphics[width=1.0\columnwidth]{img/hood.pdf}
        \caption{The comparison of the time series between the raw word \textit{hood} and the \textit{Military} related word \textit{hood}, computed on the \textit{Edinburgh twitter corpus}\cite{petrovic2012using}. The rise on July 28th, 2011 is corresponding to the event mentioned in \url{https://en.wikipedia.org/wiki/Fort_Hood\#2011_attack_plot}.}
        \label{fig:hood}
\end{figure}

The benefit of enriching the semantics for micorblogs is attractive, but it's non-trivial to transfer the knowledge restored in the knowledge base into microblog stream directly.
The existing RDF model\cite{klyne2006rdf} lacks an efficient quick mechanism to transfer the knowledge, since it's mainly designed for managing knowledge as tuples on graph. And the query on large graph is also very expensive\cite{huang2011scalable}, which is not suitable for the scene of quickly and acuaretely detecting events.
What already most meets the efficiency demand is Twevent\cite{Twevent2012}, but it's limited in filtering out meaningless microblogs by looking up Wikipedia. Some event, which contains the segments not restored in Wikipedia, may be dropped by Twevent incorrectly.

@@

\cite{dai2007transferring}.

@@

\intextsep=5pt plus 3pt minus 1pt
\begin{figure}[h]
	\setlength{\abovecaptionskip}{0.cm}
	\setlength{\belowcaptionskip}{0.cm}
	\centering
    \label{fig:subfig} %% label for entire figure
        \subfigure[]{
                \includegraphics[width=.50\columnwidth]{img/NSDetectorExample.pdf}
                \label{fig:modelDesc}

        }
        \subfigure[]{
                \includegraphics[width=.44\columnwidth]{img/initializationExample.pdf}
                \label{fig:NSinitializaton}
        }
        \caption{(a)\textsc{TransDetector}'s process flow, taking \textit{Military} related events in cyberspace as an example. \textsc{TransDetector} initializes the normal states about military from knowledge base, learns the topical words further within the time windows on the target corpus, detects events.;(b)Illustration on how to initialize history states from Wikipedia, taking \textit{Military} as an example.}
\end{figure}

@@

@@

\section{Proposed Method}
In this section, we present a novel category-level transfer learning method for event detection, namely \textsc{TransDetector}. 
Illustrated in Figure \ref{fig:modelDesc}, \textsc{TransDetector} consists of three parts: (1) extracting category-level topics in knowledge base, (2) transfer learning on category-level topics in microblog stream, (3) detecting events from category-level word time series.
\begin{comment}
Knowledge base often contains much information about what happened. 
But the existing RDF model\cite{klyne2006rdf} on knowledge base lacks an efficient mechanism to transfer the information from knowledge base to text stream.  
With the help of knowledge base's structure (detailed in sec \ref{subsec:hs_initialization}), we provide a  lightweight model to transfer the information in knowledge base to text stream.

@@

After processing each time window's data, the words in microblogs can be enriched semantically with knowledge base.
In this way, the transfer learning model provides richer semantics and less noise for microblog stream, which promotes the accuracy of event detection significantly. 
The following definitions are the concepts used by the transfer learning model \textsc{TransDetector}. 
\end{comment}

@@

\begin{table}
\setlength{\abovecaptionskip}{0.cm}%set the distance between caption and table to 0 cm.
\setlength{\belowcaptionskip}{0.cm}
\centering
\caption{Events about \textit{military} detected by systems between 2011-07-22 and 2011-07-28}
\label{my-label}
\scalebox{0.76}{
\begin{threeparttable}  
\begin{tabular}{|c|l|l|c|c|c|c|c|c|c|}
\hline
\multirow{2}{*}{Date} & \multirow{2}{*}{Event key words} & \multirow{2}{*}{Representative event tweet} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Number of \\ event tweet\end{tabular}} & \multicolumn{6}{c|}{Methods\tnote{a}} \\ \cline{5-10} 
 &  &  &  & L & TU & TW & E & B & TD \\ \hline
7/22/11 & \begin{tabular}[c]{@{}l@{}}Norway, Oslo,\\ attacks, bombing\end{tabular} & \begin{tabular}[c]{@{}l@{}}Terror Attacks Devastate Norway: A bomb ripped through \\ government offices in Oslo and a gunman... http://dlvr.it/cLbk8\end{tabular} & 557 & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\ \hline
7/23/11 & Gunman, rink & \begin{tabular}[c]{@{}l@{}}Gunman Kills Self, 5 Others at Texas Roller Rink \\ http://dlvr.it/cLcTH\end{tabular} & 43 & - & - & \checkmark &  \checkmark & - & \checkmark \\ \hline
7/26/11 & \begin{tabular}[c]{@{}l@{}}Kandahar, mayor, \\ suicide, attack\end{tabular} & \begin{tabular}[c]{@{}l@{}}TELEGRAPH{]}: Kandahar mayor killed by Afghan suicide \\ bomber: The mayor of Kandahar, the biggest city in south \_\end{tabular} & 47 & \checkmark & - & \checkmark & \checkmark & - & \checkmark \\ \hline
7/28/11 & Ft., Hood, attack & Possible Ft. Hood Attack Thwarted http://t.co/BSJ33hk & 52 & - & - & - & - & - & \checkmark \\ \hline
7/28/11 & \begin{tabular}[c]{@{}l@{}}Libyan, rebel, \\ gunned\end{tabular} & \begin{tabular}[c]{@{}l@{}}Libyan rebel chief gunned down in Benghazi \\ http://sns.mx/prfvy1\end{tabular} & 44 & - & - & - & - & - & \checkmark \\ \hline
\end{tabular}
